Sequential rank agreement methods for comparison of lists

### 2015-08-09 latex/paper.Rnw
Kommentarer

Finally, we have --- whenever possible --- used as much information
from the lists as possible, i.e., we have used all available ranks.
%% Claus: hvad vil du sige med den sidste saetning?
We could choose to censor the rankings of all the items that were
deemed not to be significant if information on both rankings and the
corresponding evidence for significance was available. That would
ensure that there would be put less emphasis on the agreement of the
non-significant items and it would be easier to identify a change in
agreement among the items that were deemed to relevant. In our
application section we have successfully introduced such an artificial
censoring for the predictor rankings obtained with ridge regression.

@@

%% In conclusion we have introduced a method for evaluation of ranked
%% (censored) lists that can be easily interpreted and that can be
%% applied to a large number of situations.
%% CLAUS: den sidste saetning er bar en omformulering af Diskussionen's foerste saetning.

%% The method here proposed can be adapted further by using it to
%% identify and cluster statistical analysis methods that provide more or
%% less the same agreement,
%% Claus: det er enten for kort eller for lang

%% or by using the rank agreement to optimize a
%% hyper-parameter in, say, elastic net regularized regression where the
%% rank agreement is used to determine the mixing proportion between the
%% $L_1$ and the $L_2$ penalty.
%% Claus: det er enten for kort eller for lang

%% Finally, the proposed method may be
%% adapted (with some additional assumptions) to the situation where the
%% lists are subsets of each other.
%% Claus: det er enten for kort eller for lang

%% We will be investigating these
%% extensions further in the future.

>>>>

Finally, we have --- whenever possible --- used all available ranks
from the lists.  We could choose to censor the rankings of all the
items that were deemed not to be significant if information on both
rankings and the corresponding evidence for significance was
available. That would ensure that there would be put less emphasis on
the agreement of the non-significant items and it would be easier to
identify a change in agreement among the items that were deemed to
relevant. In our application section we have successfully introduced
such an artificial censoring for the predictor rankings obtained with
ridge regression.

@@

In conclusion we have introduced a method for evaluation of ranked
(censored) lists that can be easily interpreted and that can be
applied to a large number of situations.  The method presented here
can be adapted further by using it to compare and classify statistical
analysis methods that agree on the rankings they provide or by using
the rank agreement to optimize a hyper-parameter in, say, elastic net
regularized regression where the rank agreement is used to determine
the mixing proportion between the $L_1$ and the $L_2$ penalty.
%Finally, the proposed method may be adapted (with some additional
%assumptions) to the situation where the lists are subsets of each
%other.  
We will be investigating these extensions further in the future.
